TRITON: Globally Consistent Sim-to-Real Transfer

### 2022-06-02 CORL/example.tex
Added data section

>>>>

\section{Data}
\label{sec:data}

\begin{figure}
	\begin{center}
		\includegraphics[width=270pt]{uvl_explanation.pdf}
	\end{center}
	\caption{
		This diagram shows the purpose of a UVL image.
		 A UVL scene is an image that has three channels: RGB.
		 R and G are used for U and V, and B is used for L.
		 L stands for Label, and determines which part of the synthetic image will get which texture.
		 The U and V coordinates correspond to positions on each texture,
		 	telling it how to project the textures onto the 3d objects represented in the UVL scene.
		The darkest shade of blue corresponds to the 1st texture, and the next darkest shade of blue corresponds to the 2nd texture etc.
		}
	\label{fig:uvl_explanation}
\end{figure}

In this paper, we'll mostly focus on a dataset that involves three alphabet blocks that are moved across a table.
Alphabet blocks were chosen because they all have the same geometry (a cube), but have very distinct semantic textures that will make temporal inconsistency obvious to the human eye.
This dataset is analagous to data that would be collected for a third-person robotic grasping task.
However, other objects (such as cans of soda, apples, cloves of garlic etc) are also for generating other results in this paper. ((TODO: Detail the five object tests and five cube tests and other stuff like shiny cans etc)).

There are two components to this dataset: Simulated data in the form of UVL scenes, and photographs.
The camera in the simulation is positioned in approximately the same place as the real camera, with approximately the same field of view.
In both domains of this dataset, the camera never moves. Instead, the objects are randomly positioned and rotated on the table.
In both the simulation and in real life, these objects are randomly translated along the x and y axis of the table, as well as rotated on the z axis.

There are 200 photographs in this datset, and they are recorded as RGB jpg images.
There are 3000 synthetic images in this dataset, in the form of UVL images.
These UVL images are also encoded as RGB images, but provide information about the geometry of a scene.
UVL images are composed of both a UV map and a label map, and are summarized in figure \ref{fig:uvl_explanation}.
To avoid positional rounding errors, UVL images are encoded as EXR files: an image format that supports floating point values.
